### 2018-03-01 manuscript.rmd
updated supp. info, bib file

Understanding the unique ecology, morphology, and development of siphonophores requires a well-resolved phylogeny of the group. The relationship of siphonophores to other hydrozoans has been difficult to determine [@cartwright2010character; @Cartwright2008kl; @zapata2015phylogenomic], but there has been progress on their internal relationships. A phylogeny [@Dunn:2005dy] based on two genes (16S, 18S) from 52 siphonophore taxa addressed several long standing questions about siphonophore biology, including the relationships of the three historically recognised groups, Cystonectae, Physonectae, and Calycophorae. Cystonectae was found to be sister to all other siphonophores, while Calycophorae were nested within "Physonectae". The name Codonophora was given to this clade of "Physonectae" and Calycophorae [@Dunn:2005dy].

@@

Specimens were collected in the north-eastern Pacific Ocean, Mediterranean, and the Gulf of California (see table 1). Collection data on all examined specimens, a description of the tissue that was sampled from the colony, collection mode, sample processing details, mRNA extraction methods, sequencing library preparation methods, and sequencing details are summarized in the file Supplementary data 1 (also found in the git repository). Monterey Bay and Gulf of California specimens were collected by remotely operated underwater vehicle (ROV) or during blue-water SCUBA dives. *Chelophyes appendiculata* and *Hippopodius hippopus* (Fig. 1C) specimens were collected in the bay of Villefranche-sur-Mer, France, during a plankton trawl on 13 April 2011. Available physical vouchers have been deposited at the Museum of Comparative Zoology (Harvard University), Cambridge, MA, the Peabody Museum of Natural History (Yale University), New Haven, CT, or had been previously deposited at the United States National Museum (Smithsonian Institution), Washington, DC. Accession numbers are given in Supplementary data 1. In cases where physical vouchers were unavailable we provide photographs to document species identity (see git repository).

@@

New data were analysed in conjunction with 14 publicly available datasets, with a total number of 43 species. Sequence assembly, annotation, homology evaluation, gene tree construction, parsing of genes trees to isolate orthologous sequences, and supermatrix construction were conducted with Agalma v. 1.0.0 [@Dunn:2013kw; @Guang202416].  This workflow integrates a variety of existing tools [@grabherr2011full; @altschul1990basic; @doi:10.1093/nar/30.7.1575; @sukumaran2010dendropy; @langmead2012fast; @li2011rsem; @talavera2007improvement; @li2009sequence; @katoh2013mafft] and new methods. Maximum likelihood analyses of the supermatrix were conducted with RAxML v 8.2.0 [@stamatakis2006raxml] and implemented via Agalma. Bayesian Inference (BI) analyses of the supermatrix were conducted using Phylobayes v. 1.7a-mpi [@lartillot2009phylobayes]. Sequence alignments, sampled and consensus trees, and voucher information are available in the git repository. Tree figures were rendered with ggtree [@Yu:2016fo].

@@

```{r specimen_summary, results='asis', echo=FALSE, comment=NA, warning=FALSE}
specimen_data <- read.csv("supplementary_info/Supplementary_data_1_Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth (m)","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")

specimen_data_reduced <- specimen_data[,c(1,2,4,14,16)]
specimen_data_reduced$`New data`<-sub("^N"," ",specimen_data_reduced$`New data`)

specimen_data_reduced<-as.data.frame(specimen_data_reduced)
xtable_specimen<-xtable(specimen_data_reduced,auto=TRUE, caption="A complete list of specimens collected for this work. New data indicated by Y, blank fields indicate that data were already published.")
print(xtable_specimen,comment=F, include.rownames=FALSE, scalebox='0.7')

>>>>

Understanding the unique ecology, morphology, and development of siphonophores requires a well-resolved phylogeny of the group. The relationship of siphonophores to other hydrozoans has been difficult to determine [@cartwright2010character; @Cartwright2008kl; @zapata2015phylogenomic; @kayal2015phylogenetic], but there has been progress on their internal relationships. A phylogeny [@Dunn:2005dy] based on two genes (16S, 18S) from 52 siphonophore taxa addressed several long standing questions about siphonophore biology, including the relationships of the three historically recognised groups, Cystonectae, Physonectae, and Calycophorae. Cystonectae was found to be sister to all other siphonophores, while Calycophorae were nested within "Physonectae". The name Codonophora was given to this clade of "Physonectae" and Calycophorae [@Dunn:2005dy].

@@

Specimens were collected in the north-eastern Pacific Ocean, Mediterranean, and the Gulf of California (see table 1). Collection data on all examined specimens, a description of the tissue that was sampled from the colony, collection mode, sample processing details, mRNA extraction methods, sequencing library preparation methods, and sequencing details are summarized in the file Supplementary data 1 (also found in the git repository). Monterey Bay and Gulf of California specimens were collected by remotely operated underwater vehicle (ROV) or during blue-water SCUBA dives. *Chelophyes appendiculata* and *Hippopodius hippopus* (Fig. 1C) specimens were collected in the bay of Villefranche-sur-Mer, France, during a plankton trawl on 13 April 2011. Available physical vouchers have been deposited at the Museum of Comparative Zoology (Harvard University), Cambridge, MA, the Peabody Museum of Natural History (Yale University), New Haven, CT, or had been previously deposited at the Smithsonian National Museum of Natural History, Washington, DC. Accession numbers are given in Supplementary data 1. In cases where physical vouchers were unavailable we provide photographs to document species identity (see git repository: https://github.com/caseywdunn/siphonophore_phylogeny_2017/tree/master/supplementary_info/photographic_vouchers).

@@

New data were analysed in conjunction with 14 publicly available datasets [@zapata2015phylogenomic, @Dunn:2013kw, @lehnert2012developing, @philippe2009phylogenomics, @fidler2014unique, @chapman2010dynamic, @sanders2014differential, @putnam2007sea, @sanders2015interspecific], with a total number of 43 species. Sequence assembly, annotation, homology evaluation, gene tree construction, parsing of genes trees to isolate orthologous sequences, and supermatrix construction were conducted with Agalma v. 1.0.0 [@Dunn:2013kw; @Guang202416].  This workflow integrates a variety of existing tools [@grabherr2011full; @altschul1990basic; @doi:10.1093/nar/30.7.1575; @sukumaran2010dendropy; @langmead2012fast; @li2011rsem; @talavera2007improvement; @li2009sequence; @katoh2013mafft] and new methods. Maximum likelihood analyses of the supermatrix were conducted with RAxML v 8.2.0 [@stamatakis2006raxml] and implemented via Agalma. Bayesian Inference (BI) analyses of the supermatrix were conducted using Phylobayes v. 1.7a-mpi [@lartillot2009phylobayes]. Sequence alignments, sampled and consensus trees, and voucher information are available in the git repository. Tree figures were rendered with ggtree [@Yu:2016fo].

@@

```{r specimen_summary, results='asis', echo=FALSE, comment=NA, warning=FALSE}
specimen_data <- read.csv("supplementary_info/Supplementary_data_1_Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Identified by","Collection date","Specimen id","Depth (m)","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")

specimen_data_reduced <- specimen_data[,c(1,2,15,17,4)]
specimen_data_reduced$`New data`<-sub("^N"," ",specimen_data_reduced$`New data`)

specimen_data_reduced<-as.data.frame(specimen_data_reduced)
xtable_specimen<-xtable(specimen_data_reduced,auto=TRUE, caption="A complete list of specimens used in this work, information from already published datasets added where available. New data indicated by Y, blank fields indicate that data were already published. For the species not on SRA, a link to the data is included in supplementary file 1.")
print(xtable_specimen,comment=F, include.rownames=FALSE, scalebox='0.7')
